---
title: "Analysis_revisions"
author: "Matt Wuensch"
date: "2025-02-07"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r}
library(glmmTMB)
library(DHARMa)
library(vegan)
library(ggplot2)
library(patchwork)
library(performance)
library(dplyr)
library(tidyr)
library(ncf)

# Bringing in data that you'll need
detections.dat <- read.csv("detection.data.csv")
evi.500.wa <- read.csv("EVI.500m.csv")

# Add in EVI WA for 500 m
detections.dat.500 <- detections.dat %>%
  right_join(evi.500.wa, by = c("Station", "time.code"))

# Filter out unneeded columns
detections.dat.500 <- detections.dat.500 %>%
  select(-days.available, -days.inactive, -X, -season)

latlong.dat <- read.csv("cmp_all_camera_covariates.csv")
names(latlong.dat)[names(latlong.dat) == 'camera_id'] <- 'Station'
latlong.dat$Station <- as.factor(latlong.dat$Station)
levels(latlong.dat$Station)

detections.dat.500$Station <- as.factor(detections.dat.500$Station)
levels(detections.dat.500$Station)

# Bring in the landcover data, clean it up and merge it to detections df
landco.500 <- read.csv("LF.500m.csv")

# There are duplicates for each landco type from when you summarized them in arc. use distinct function to rein that in
landco.dist.500 <- landco.500 %>%
  distinct(Subcl_Veg, camera_id, SUM_Shape_)

# Rename each column to be easier
landco.dist.500 <- landco.dist.500 %>%
  rename("Veg.cover" = "Subcl_Veg",
         "Station" = "camera_id",
         "Area" = "SUM_Shape_") #Unit is in m
# Split it wide
landco.wide.500 <- landco.dist.500 %>%
  spread(Veg.cover, Area)

# Renaming cover classes
colnames(landco.wide.500)[2:22] = c("temperate.boreal.forest.shrub", "temperate.boreal.forest.tree", "temperate.boreal.grassland.herbaceous", "temperate.boreal.grassland.shrub", "shrub.herb.wetland.herbaceous", "shrub.herb.wetland.shrub", "shrub.herb.wetland.tree", "woody.ag.tree", "herb.ag.agriculture", "herb.ag.herbaceous", "herb.woody.developed.herbaceous", "herbaceous.woody.developed.shrub", "herbaceous.woody.developed.tree", "developed.high", "developed.low", "developed.medium", "road", "water", "quarry", "recent.disturbed.herbaceous", "recent.disturbed.tree")

# set nas to 0
landco.wide.500[is.na(landco.wide.500)] <- 0

# Making landco into proportion of the 500 m radius area around the camera trap
rowsums.500 <-apply(landco.wide.500[,2:22], 1, sum)
lcprop.500 <- landco.wide.500[,2:22]/772542.5
landco.b.500 <- cbind(landco.wide.500[,1], lcprop.500)
landco.b.500 <- as.data.frame(landco.b.500)
names(landco.b.500)[names(landco.b.500) == 'landco.wide.500[, 1]'] <- 'Station'

#merge landco to detections
detections.dat.500 <- detections.dat.500 %>%
  right_join(landco.b.500, by = "Station")

# Coyotes needs to be in coyotes/camera day rather than raw coyote detections to match the offset
detections.dat.500$coyote.day <- detections.dat.500$Coyote.det/detections.dat.500$days.active

# relocate column
detections.dat.500 <- detections.dat.500 %>%
  relocate(coyote.day, .after = Coyote.det)

# Drop away all 0 days active observations...because that makes no sense to include these
detections.dat.500 <- detections.dat.500 %>%
  filter(!days.active == 0)

# Combine columns for only landcover, no vegetation cover. May use, may not but good to have, may need to do some more later on, but for now this will work
detections.dat.500$temperate.boreal.forest <- detections.dat.500$temperate.boreal.forest.shrub + detections.dat.500$temperate.boreal.forest.tree

detections.dat.500$temperate.boreal.grassland <- detections.dat.500$temperate.boreal.grassland.herbaceous + detections.dat.500$temperate.boreal.grassland.shrub

detections.dat.500$shrub.herb.wetland <- detections.dat.500$shrub.herb.wetland.herbaceous + detections.dat.500$shrub.herb.wetland.shrub + detections.dat.500$shrub.herb.wetland.tree

detections.dat.500$herbaceous.agriculture <- detections.dat.500$herb.ag.agriculture + detections.dat.500$herb.ag.herbaceous

detections.dat.500$herbaceous.woody.developed <- detections.dat.500$herb.woody.developed.herbaceous + detections.dat.500$herbaceous.woody.developed.shrub + detections.dat.500$herbaceous.woody.developed.tree 

detections.dat.500$agriculture <- detections.dat.500$herbaceous.agriculture + detections.dat.500$woody.ag.tree


detections.dat.500$developed <- detections.dat.500$developed.high + detections.dat.500$developed.low + detections.dat.500$developed.medium

detections.dat.500$developed.lowmed <- detections.dat.500$developed.low +detections.dat.500$developed.medium


### Model
# Subset by phase 
ru.dat.500 <- detections.dat.500 %>%
  filter(phase == "rut") %>%
  droplevels()

wi.dat.500 <- detections.dat.500 %>%
  filter(phase == "winter.forage")

fa.dat.500 <- detections.dat.500 %>%
  filter(phase == "fawning")

su.dat.500 <- detections.dat.500 %>%
  filter(phase == "summer.forage")

#### Centering and scaling all of your dfs
# Create new df that contains centered and scaled covars for each model
ru.cs.500 <- as.data.frame(scale(ru.dat.500[c("coyote.day", "evi.500.wa" , "temperate.boreal.grassland" , "shrub.herb.wetland", "woody.ag.tree", "herbaceous.agriculture", "herbaceous.woody.developed", "developed.lowmed", "developed.high", "road", "water")], center = TRUE, scale = TRUE))

wi.cs.500 <- as.data.frame(scale(wi.dat.500[c("coyote.day", "evi.500.wa" , "temperate.boreal.grassland" , "shrub.herb.wetland", "woody.ag.tree", "herbaceous.agriculture", "herbaceous.woody.developed", "developed.lowmed", "developed.high", "road", "water")], center = TRUE, scale = TRUE))

fa.cs.500 <- as.data.frame(scale(fa.dat.500[c("coyote.day", "evi.500.wa" , "temperate.boreal.grassland" , "shrub.herb.wetland", "woody.ag.tree", "herbaceous.agriculture", "herbaceous.woody.developed", "developed.lowmed", "developed.high", "road", "water")], center = TRUE, scale = TRUE))

su.cs.500 <- as.data.frame(scale(su.dat.500[c("coyote.day", "evi.500.wa" , "temperate.boreal.grassland" , "shrub.herb.wetland", "woody.ag.tree", "herbaceous.agriculture", "herbaceous.woody.developed", "developed.lowmed", "developed.high", "road", "water")], center = TRUE, scale = TRUE))

# Bind the c&s df to needed data from original df
ru.cs.df.500 <- cbind(ru.dat.500[c("Station", "Deer.det", "days.active")], ru.cs.500)

wi.cs.df.500 <- cbind(wi.dat.500[c("Station", "Deer.det", "days.active")], wi.cs.500)

fa.cs.df.500 <- cbind(fa.dat.500[c("Station", "Deer.det", "days.active")], fa.cs.500)

su.cs.df.500 <- cbind(su.dat.500[c("Station", "Deer.det", "days.active")], su.cs.500)


# Get total number of detections for each period

(sum(detections.dat.500$days.active)) #74449 total
(sum(ru.dat.500$days.active)) #19260
(sum(wi.dat.500$days.active)) #19490
(sum(fa.dat.500$days.active)) #17160
(sum(su.dat.500$days.active)) #18539

(sum(detections.dat.500$Deer.det)) #45942 total
(sum(ru.dat.500$Deer.det)) #16697
(sum(wi.dat.500$Deer.det)) #8595
(sum(fa.dat.500$Deer.det)) #9458
(sum(su.dat.500$Deer.det)) #11192

(sum(detections.dat.500$Coyote.det)) #4079
(sum(ru.dat.500$Coyote.det)) #1229
(sum(wi.dat.500$Coyote.det)) #1288
(sum(fa.dat.500$Coyote.det)) #746
(sum(su.dat.500$Coyote.det)) #816


# Adding lat/long data to each df
ru.cs.df.500 <- ru.cs.df.500 %>%
  right_join(latlong.dat[c("Station", "latitude", "longitude")], by = "Station")

ru.cs.df.500 <- ru.cs.df.500 %>%
  filter(!Station %in% c("BE1140", "BE1144")) %>% # filtering out levels that were inactive
  droplevels()


wi.cs.df.500 <- wi.cs.df.500 %>%
  right_join(latlong.dat[c("Station", "latitude", "longitude")], by = "Station")

wi.cs.df.500 <- wi.cs.df.500 %>%
  filter(!Station %in% c("BE1140", "BE1144", "BK1088")) %>% # filtering out levels that were inactive
  droplevels()

fa.cs.df.500 <- fa.cs.df.500 %>%
  right_join(latlong.dat[c("Station", "latitude", "longitude")], by = "Station")

fa.cs.df.500 <- fa.cs.df.500 %>%
  filter(!Station %in% c("BE1140", "BE1144")) %>% # filtering out levels that were inactive
  droplevels()


su.cs.df.500 <- su.cs.df.500 %>%
  right_join(latlong.dat[c("Station", "latitude", "longitude")], by = "Station")

su.cs.df.500 <- su.cs.df.500 %>%
  filter(!Station %in% c("BE1140", "BE1144")) %>% # filtering out levels that were inactive
  droplevels()


# Nbm. Full models containing temperate boreal forest and roads exhibited colinearity and were removed. Water was removed due to it being non-suitable habitat for white-tailed deer
nbm.ru.zif.500 <- glmmTMB(Deer.det ~coyote.day+ evi.500.wa + temperate.boreal.grassland+ shrub.herb.wetland+ woody.ag.tree+ herbaceous.agriculture+ herbaceous.woody.developed+ developed.lowmed + developed.high + offset(log(days.active)) + (1|Station), ziformula = ~1, data = ru.cs.df.500, family = nbinom2)

nbm.wi.zif.500 <- glmmTMB(Deer.det ~ coyote.day+ evi.500.wa + temperate.boreal.grassland+ shrub.herb.wetland+ woody.ag.tree+ herbaceous.agriculture+ herbaceous.woody.developed+ developed.lowmed + developed.high + offset(log(days.active)) + (1|Station), ziformula = ~1,  data = wi.cs.df.500, family = nbinom2)

nbm.fa.zif.500 <- glmmTMB(Deer.det ~ coyote.day+ evi.500.wa + temperate.boreal.grassland+ shrub.herb.wetland+ woody.ag.tree+ herbaceous.agriculture+ herbaceous.woody.developed+ developed.lowmed + developed.high + offset(log(days.active)) + (1|Station), ziformula = ~1,  data = fa.cs.df.500, family = nbinom2)

nbm.su.zif.500 <- glmmTMB(Deer.det ~ coyote.day+ evi.500.wa + temperate.boreal.grassland+ shrub.herb.wetland+ woody.ag.tree+ herbaceous.agriculture+ herbaceous.woody.developed+ developed.lowmed + developed.high + offset(log(days.active)) + (1|Station), ziformula = ~1, data = su.cs.df.500, family = nbinom2)

# Check for collinearity. Temperate and boreal forests were highly collinear, without though, everything checks out. Pulled roads from analysis because they had a high vif and were correlated with developed.lowmed in correlation plots (See bottom of code)
check_collinearity(nbm.ru.zif.500)
check_collinearity(nbm.wi.zif.500)
check_collinearity(nbm.fa.zif.500)
check_collinearity(nbm.su.zif.500)

# Model summary
summary(nbm.ru.zif.500)
summary(nbm.wi.zif.500)
summary(nbm.fa.zif.500)
summary(nbm.su.zif.500)

# Simulate the residuals via dharma
simulationOutput.zif.ru.500 <- simulateResiduals(fittedModel = nbm.ru.zif.500, plot = F, n = 5000)
simulationOutput.zif.wi.500 <- simulateResiduals(fittedModel = nbm.wi.zif.500, plot = F, n = 5000)
simulationOutput.zif.fa.500 <- simulateResiduals(fittedModel = nbm.fa.zif.500, plot = F, n = 5000)
simulationOutput.zif.su.500 <- simulateResiduals(fittedModel = nbm.su.zif.500, plot = F, n = 5000)

# inspect your residuals for issues in fit. First check overall plots, then fit residuals against covariates per the recommendation of Florian Hartig

# Covars: coyote.day, evi.500.wa, temperate.boreal.grassland, shrub.herb.wetland, woody.ag.tree, herbaceous.agriculture, herbaceous.woody.developed, developed.lowmed, developed.high, Station
plot(simulationOutput.zif.ru.500)
plotResiduals(simulationOutput.zif.ru.500, ru.cs.df.500$coyote.day)

plot(simulationOutput.zif.wi.500)
plotResiduals(simulationOutput.zif.wi.500, wi.cs.df.500$coyote.day)

plot(simulationOutput.zif.fa.500)
plotResiduals(simulationOutput.zif.fa.500, fa.cs.df.500$coyote.day)

plot(simulationOutput.zif.su.500)
plotResiduals(simulationOutput.zif.su.500, su.cs.df.500$coyote.day)

# Spline correlograms for supplement
ru.Correlog.Glm <- spline.correlog(
  x = ru.cs.df.500$longitude,
  y = ru.cs.df.500$latitude,
  z = residuals(nbm.ru.zif.500, type = "pearson"),
  latlon = T)

wi.Correlog.Glm <- spline.correlog(
  x = wi.cs.df.500$longitude,
  y = wi.cs.df.500$latitude,
  z = residuals(nbm.wi.zif.500, type = "pearson"),
  latlon = T)

fa.Correlog.Glm <- spline.correlog(
  x = fa.cs.df.500$longitude,
  y = fa.cs.df.500$latitude,
  z = residuals(nbm.fa.zif.500, type = "pearson"),
  latlon = T)

su.Correlog.Glm <- spline.correlog(
  x = su.cs.df.500$longitude,
  y = su.cs.df.500$latitude,
  z = residuals(nbm.su.zif.500, type = "pearson"),
  latlon = T)

# Making the plots
plot(ru.Correlog.Glm)
plot(wi.Correlog.Glm)
plot(fa.Correlog.Glm)
plot(su.Correlog.Glm)

png("spline_correlograms.png", width = 4200, height = 4200, res = 300)

# 2 rows x 2 columns layout
par(mfrow = c(2, 2), oma = c(4, 4, 2, 1), mar = c(4, 4, 3, 2))  # Adjust margins

# Plot each season with custom title
plot(ru.Correlog.Glm, main = "Pre-rut/rut", xlab = "Distance (km)", ylab = "Correlation", 
     cex.axis = 1.4,   # Axis ticks larger
     cex.lab = 1.6,    # Axis labels larger
     cex.main = 1.8)    # Title larger
plot(wi.Correlog.Glm, main = "Winter forage", xlab = "Distance (km)", ylab = "",
     cex.axis = 1.4,   # Axis ticks larger
     cex.lab = 1.6,    # Axis labels larger
     cex.main = 1.8)   # Title larger
plot(fa.Correlog.Glm, main = "Fawning", xlab = "Distance (km)", ylab = "Correlation",
     cex.axis = 1.4,   # Axis ticks larger
     cex.lab = 1.6,    # Axis labels larger
     cex.main = 1.8)   # Title larger
plot(su.Correlog.Glm, main = "Summer forage", xlab = "Distance (km)", ylab = "",
     cex.axis = 1.4,   # Axis ticks larger
     cex.lab = 1.6,    # Axis labels larger
     cex.main = 1.8)   # Title larger

dev.off()

```
# In the initial model, we included 2 covariates that had high vifs and were colinear: Temperate and boreal forests and roads. Temperate and boreal forests was colinear with herbaceous and woody developed, roads was with developed.lowmed. Run correlations to identify the relationship between these covariates and white-tailed deer detection rates for each season to decide which covariates to retain. Ultimately, this was checked as an alternative, but the previous chunk contains the models you will use.
```{r}
# Set new dfs for correlations
ru.dat.500.2 <- ru.dat.500 %>%
  select(Deer.det, temperate.boreal.forest, herbaceous.woody.developed, road, developed.lowmed)

wi.dat.500.2 <- wi.dat.500 %>%
  select(Deer.det, temperate.boreal.forest, herbaceous.woody.developed, road, developed.lowmed)

fa.dat.500.2 <- fa.dat.500 %>%
  select(Deer.det, temperate.boreal.forest, herbaceous.woody.developed, road, developed.lowmed)

su.dat.500.2 <- su.dat.500 %>%
  select(Deer.det, temperate.boreal.forest, herbaceous.woody.developed, road, developed.lowmed)

# Get pearson correlations
ru.cors = cor(ru.dat.500.2, method = "pearson") # Stronger - correlation with tbf than + hwd, stronger + dev.lm than + road
wi.cors = cor(wi.dat.500.2, method = "pearson") # Stronger - correlation with tbf than + hwd, stronger + dev.lm than + road
fa.cors = cor(fa.dat.500.2, method = "pearson") # Stronger - correlation with tbf than + hwd, stronger + dev.lm than + road
su.cors = cor(su.dat.500.2, method = "pearson") # Stronger - correlation with tbf than + hwd, stronger + dev.lm than + road

# Correlations indicate that we should include temperate boreal forests and developed low.med



#### Rerunning models with temperate boreal forest subbed in.
# Create new df that contains centered and scaled covars for each model
ru.cs.500.2 <- as.data.frame(scale(ru.dat.500[c("coyote.day", "evi.500.wa" , "temperate.boreal.grassland" , "shrub.herb.wetland", "woody.ag.tree", "herbaceous.agriculture", "temperate.boreal.forest", "developed.lowmed", "developed.high", "road", "water")], center = TRUE, scale = TRUE))

wi.cs.500.2 <- as.data.frame(scale(wi.dat.500[c("coyote.day", "evi.500.wa" , "temperate.boreal.grassland" , "shrub.herb.wetland", "woody.ag.tree", "herbaceous.agriculture", "temperate.boreal.forest", "developed.lowmed", "developed.high", "road", "water")], center = TRUE, scale = TRUE))

fa.cs.500.2 <- as.data.frame(scale(fa.dat.500[c("coyote.day", "evi.500.wa" , "temperate.boreal.grassland" , "shrub.herb.wetland", "woody.ag.tree", "herbaceous.agriculture", "temperate.boreal.forest", "developed.lowmed", "developed.high", "road", "water")], center = TRUE, scale = TRUE))

su.cs.500.2 <- as.data.frame(scale(su.dat.500[c("coyote.day", "evi.500.wa" , "temperate.boreal.grassland" , "shrub.herb.wetland", "woody.ag.tree", "herbaceous.agriculture", "temperate.boreal.forest", "developed.lowmed", "developed.high", "road", "water")], center = TRUE, scale = TRUE))

# Bind the c&s df to needed data from original df
ru.cs.df.500.2 <- cbind(ru.dat.500[c("Station", "Deer.det", "days.active")], ru.cs.500.2)

wi.cs.df.500.2 <- cbind(wi.dat.500[c("Station", "Deer.det", "days.active")], wi.cs.500.2)

fa.cs.df.500.2 <- cbind(fa.dat.500[c("Station", "Deer.det", "days.active")], fa.cs.500.2)

su.cs.df.500.2 <- cbind(su.dat.500[c("Station", "Deer.det", "days.active")], su.cs.500.2)

# Nbm
nbm.ru.zif.500.2 <- glmmTMB(Deer.det ~coyote.day+ evi.500.wa + temperate.boreal.grassland+ shrub.herb.wetland+ woody.ag.tree+ herbaceous.agriculture+ temperate.boreal.forest+ developed.lowmed + developed.high + offset(log(days.active)) + (1|Station), ziformula = ~1, data = ru.cs.df.500.2, family = nbinom2)

nbm.wi.zif.500.2 <- glmmTMB(Deer.det ~ coyote.day+ evi.500.wa + temperate.boreal.grassland+ shrub.herb.wetland+ woody.ag.tree+ herbaceous.agriculture+ temperate.boreal.forest+ developed.lowmed + developed.high  + offset(log(days.active)) + (1|Station), ziformula = ~1,  data = wi.cs.df.500.2, family = nbinom2)

nbm.fa.zif.500.2 <- glmmTMB(Deer.det ~ coyote.day+ evi.500.wa + temperate.boreal.grassland+ shrub.herb.wetland+ woody.ag.tree+ herbaceous.agriculture+ temperate.boreal.forest+ developed.lowmed + developed.high  + offset(log(days.active)) + (1|Station), ziformula = ~1,  data = fa.cs.df.500.2, family = nbinom2)

nbm.su.zif.500.2 <- glmmTMB(Deer.det ~ coyote.day+ evi.500.wa + temperate.boreal.grassland+ shrub.herb.wetland+ woody.ag.tree+ herbaceous.agriculture+ temperate.boreal.forest+ developed.lowmed + developed.high  + offset(log(days.active)) + (1|Station), ziformula = ~1, data = su.cs.df.500.2, family = nbinom2)

# Check for collinearity, did this with temperate boreal forest and it was HORRENDOUS, without, everything checks out. Pulled roads from analysis because they had a high vif and were correlated with developed.lowmed in correlation plots (See bottom of code)
check_collinearity(nbm.ru.zif.500.2)
check_collinearity(nbm.wi.zif.500.2)
check_collinearity(nbm.fa.zif.500.2)
check_collinearity(nbm.su.zif.500.2)

# The issue here is that when including temperate boreal forests, it is colinear with other covariates as well, likely due to it's strong negative correlation with all other sites. Run a correlation of all covariates to exhibit this and retain your original model.
```
# Building effects size plots

```{r}
# Make your summaries into objects
summary.ru.500 <- summary(nbm.ru.zif.500)
summary.wi.500 <- summary(nbm.wi.zif.500)
summary.fa.500 <- summary(nbm.fa.zif.500)
summary.su.500 <- summary(nbm.su.zif.500)

# Pull the parts of the objects you'll need and make them dfs
summary.ru.df.500 <- as.data.frame(summary.ru.500$coefficients$cond)
summary.wi.df.500 <- as.data.frame(summary.wi.500$coefficients$cond)
summary.fa.df.500 <- as.data.frame(summary.fa.500$coefficients$cond)
summary.su.df.500 <- as.data.frame(summary.su.500$coefficients$cond) 

#pull the zi
#summary.ru.zi.df.500 <- as.data.frame(summary.ru.500$coefficients$zi)
#summary.wi.zi.df.500 <- as.data.frame(summary.wi.500$coefficients$zi)
#summary.fa.zi.df.500 <- as.data.frame(summary.fa.500$coefficients$zi)
#summary.su.zi.df.500 <- as.data.frame(summary.su.500$coefficients$zi) 

# renaming process, bind the dfs
#summary.ru.df.500 <- rbind(summary.ru.df.500,summary.ru.zi.df.500)
#summary.wi.df.500 <- rbind(summary.wi.df.500,summary.wi.zi.df.500)
#summary.fa.df.500 <- rbind(summary.fa.df.500,summary.fa.zi.df.500)
#summary.su.df.500 <- rbind(summary.su.df.500,summary.su.zi.df.500)

#Make row names into a column
summary.ru.df.500$Covariate <- rownames((summary.ru.df.500))
summary.ru.df.500$Covariate <- as.factor(summary.ru.df.500$Covariate)

summary.wi.df.500$Covariate <- rownames((summary.wi.df.500))
summary.wi.df.500$Covariate <- as.factor(summary.wi.df.500$Covariate)

summary.fa.df.500$Covariate <- rownames((summary.fa.df.500))
summary.fa.df.500$Covariate <- as.factor(summary.fa.df.500$Covariate)

summary.su.df.500$Covariate <- rownames((summary.su.df.500))
summary.su.df.500$Covariate <- as.factor(summary.su.df.500$Covariate)

# Nulling rownames
rownames(summary.ru.df.500) <- NULL
rownames(summary.wi.df.500) <- NULL
rownames(summary.fa.df.500) <- NULL
rownames(summary.su.df.500) <- NULL

# Moving covariate to left
summary.ru.df.500 <- summary.ru.df.500 %>%
  relocate(Covariate, .before = Estimate)

summary.wi.df.500 <- summary.wi.df.500 %>%
  relocate(Covariate, .before = Estimate)

summary.fa.df.500 <- summary.fa.df.500 %>%
  relocate(Covariate, .before = Estimate)

summary.su.df.500 <- summary.su.df.500 %>%
  relocate(Covariate, .before = Estimate)


# Rename all levels of a factor
summary.ru.df.500 <- summary.ru.df.500 %>%
  dplyr::mutate(Covariate = recode(Covariate, "(Intercept)" = "Cond.(intercept)",
                                   coyote.day = "Coyote",
                                   evi.500.wa = "EVI",
                                   temperate.boreal.grassland = "Temperate boreal grassland",
                                   shrub.herb.wetland = "Herb. shrub wetland",
                                   woody.ag.tree = "Woody ag.",
                                   herbaceous.agriculture = "Herb. ag.",
                                   herbaceous.woody.developed = "Herb. woody developed",
                                   developed.lowmed = "Developed low-med",
                                   developed.high = "Developed high"
                )
  ) %>%
  filter(!Covariate == "Cond.(intercept)")


summary.wi.df.500 <- summary.wi.df.500 %>%
  dplyr::mutate(Covariate = recode(Covariate, "(Intercept)" = "Cond.(intercept)",
                                   coyote.day = "Coyote",
                                   evi.500.wa = "EVI",
                                   temperate.boreal.grassland = "Temperate boreal grassland",
                                   shrub.herb.wetland = "Herb. shrub wetland",
                                   woody.ag.tree = "Woody ag.",
                                   herbaceous.agriculture = "Herb. ag.",
                                   herbaceous.woody.developed = "Herb. woody developed",
                                   developed.lowmed = "Developed low-med",
                                   developed.high = "Developed high"
                )
  ) %>%
  filter(!Covariate == "Cond.(intercept)")


summary.fa.df.500 <- summary.fa.df.500 %>%
  dplyr::mutate(Covariate = recode(Covariate, "(Intercept)" = "Cond.(intercept)",
                                   coyote.day = "Coyote",
                                   evi.500.wa = "EVI",
                                   temperate.boreal.grassland = "Temperate boreal grassland",
                                   shrub.herb.wetland = "Herb. shrub wetland",
                                   woody.ag.tree = "Woody ag.",
                                   herbaceous.agriculture = "Herb. ag.",
                                   herbaceous.woody.developed = "Herb. woody developed",
                                   developed.lowmed = "Developed low-med",
                                   developed.high = "Developed high"
                )
  ) %>%
  filter(!Covariate == "Cond.(intercept)")



summary.su.df.500 <- summary.su.df.500 %>%
  dplyr::mutate(Covariate = recode(Covariate, "(Intercept)" = "Cond.(intercept)",
                                   coyote.day = "Coyote",
                                   evi.500.wa = "EVI",
                                   temperate.boreal.grassland = "Temperate boreal grassland",
                                   shrub.herb.wetland = "Herb. shrub wetland",
                                   woody.ag.tree = "Woody ag.",
                                   herbaceous.agriculture = "Herb. ag.",
                                   herbaceous.woody.developed = "Herb. woody developed",
                                   developed.lowmed = "Developed low-med",
                                   developed.high = "Developed high"
                )
  ) %>%
  filter(!Covariate == "Cond.(intercept)")


# Adding a column stating which season it's from
summary.ru.df.500$Model <- "Pre-rut/rut"
summary.wi.df.500$Model <- "Winter forage"
summary.fa.df.500$Model <- "Fawning"
summary.su.df.500$Model <- "Summer forage"

# Reorder factor levels
summary.ru.df.500$Covariate <- factor(summary.ru.df.500$Covariate, levels = c("Developed high", "Developed low-med", "Herb. woody developed", "Herb. ag.", "Woody ag.", "Herb. shrub wetland", "Temperate boreal grassland", "EVI", "Coyote", "Cond.(intercept)"))

summary.wi.df.500$Covariate <- factor(summary.wi.df.500$Covariate, levels = c("Developed high", "Developed low-med", "Herb. woody developed", "Herb. ag.", "Woody ag.", "Herb. shrub wetland", "Temperate boreal grassland", "EVI", "Coyote", "Cond.(intercept)"))

summary.fa.df.500$Covariate <- factor(summary.fa.df.500$Covariate, levels = c("Developed high", "Developed low-med", "Herb. woody developed", "Herb. ag.", "Woody ag.", "Herb. shrub wetland", "Temperate boreal grassland", "EVI", "Coyote", "Cond.(intercept)"))

summary.su.df.500$Covariate <- factor(summary.su.df.500$Covariate, levels = c("Developed high", "Developed low-med", "Herb. woody developed", "Herb. ag.", "Woody ag.", "Herb. shrub wetland", "Temperate boreal grassland", "EVI", "Coyote", "Cond.(intercept)"))


# Adding a significant/non-significant column.  #### CHANGE THIS TO FILL BASED ON IF/ELSE TERMS
summary.ru.df.500$Significance <- ifelse(summary.ru.df.500$'Pr(>|z|)'<= 0.05, "p < 0.05", "p > 0.05")
summary.wi.df.500$Significance <- ifelse(summary.wi.df.500$'Pr(>|z|)'<= 0.051, "p < 0.05", "p > 0.05") #p is = 0.050 for a covar, shading it as significant here and will report values in table.
summary.fa.df.500$Significance <- ifelse(summary.fa.df.500$'Pr(>|z|)'<= 0.05, "p < 0.05", "p > 0.05") 
summary.su.df.500$Significance <- ifelse(summary.su.df.500$'Pr(>|z|)'<= 0.05, "p < 0.05", "p > 0.05")

# Adding a theme that I like
theme <- theme_classic()+
  theme(axis.title.x = element_text(size = 12), axis.title.y = element_blank(), text = element_text(size = 11), axis.text=element_text(size=9, color = "black"))

# Now make effects sizes plots, and export the above as tables, and you are set!

ru.plot.500 <- ggplot(data = summary.ru.df.500, aes(x = Estimate, y = Covariate)) +
  geom_vline(xintercept = 0, color = "#9E2024", size = 1.5, alpha = .85) + 
  geom_errorbar(aes(xmax = Estimate+ `Std. Error`, xmin = Estimate-`Std. Error`, color = Significance), width = 0, size = 1) +
  geom_point(aes(color = Significance), size = 2.75) + 
  theme +
  scale_color_manual(values = c("#6F8EBA", "black")) + 
  annotate("text", x = .435, y = 9, label = "Pre-rut/rut", size = 4) +
  theme(axis.title.x = element_blank(), legend.position = "none") +
  xlim(-0.5,0.5)

wi.plot.500 <- ggplot(data = summary.wi.df.500, aes(x = Estimate, y = Covariate)) +
  geom_vline(xintercept = 0, color = "#9E2024", size = 1.5, alpha = .85) + 
  geom_errorbar(aes(xmax = Estimate+ `Std. Error`, xmin = Estimate-`Std. Error`, color = Significance), width = 0, size = 1) +
  geom_point(aes(color = Significance), size = 2.75) + 
  theme +
  scale_color_manual(values = c("#6F8EBA", "black")) +
  annotate("text", x = .418, y = 9, label = "Winter forage", size = 4) +
  theme(axis.title.x = element_blank(), legend.position = "none") +
  xlim(-0.5,0.5)


fa.plot.500 <- ggplot(data = summary.fa.df.500, aes(x = Estimate, y = Covariate)) +
  geom_vline(xintercept = 0, color = "#9E2024", size = 1.5, alpha = .85) + 
  geom_errorbar(aes(xmax = Estimate+ `Std. Error`, xmin = Estimate-`Std. Error`, color = Significance), width = 0, size = 1) +
  geom_point(aes(color = Significance), size = 2.75) + 
  theme +
  scale_color_manual(values = c("#6F8EBA", "black")) + 
  annotate("text", x = .454, y = 9, label = "Fawning", size = 4) +
  theme(legend.position = "none") +
  xlim(-0.5,0.5)

su.plot.500 <- ggplot(data = summary.su.df.500, aes(x = Estimate, y = Covariate)) +
  geom_vline(xintercept = 0, color = "#9E2024", size = 1.5, alpha = .85) + 
  geom_errorbar(aes(xmax = Estimate+ `Std. Error`, xmin = Estimate-`Std. Error`, color = Significance), width = 0, size = 1) +
  geom_point(aes(color = Significance), size = 2.75) + 
  theme +
  scale_color_manual(values = c("#6F8EBA", "black")) + 
  annotate("text", x = .4, y = 9, label = "Summer forage", size = 4) +
  theme(axis.title.x = element_blank(), legend.title = element_blank(), legend.position = c(.10, .9), legend.key.size = unit(.2,"cm"), legend.background = element_rect(size = .3, color = "black")) +
  xlim(-0.5,0.5)

# Patchwork into single plot
full.plot.500 <- su.plot.500+ru.plot.500+wi.plot.500+fa.plot.500 + plot_layout(nrow = 4)

ggsave("effects.plot.500.v3.jpg", full.plot.500, height = 9, width = 7, unit = "in", dpi = 500)

#ggsave("C:/Users/mwuen/Documents/R/CH4_cmp_collab/dissertation.figure.png", su.plot.500, height = 6, width =10)

# Write summaries into csvs for table
write.csv(summary.ru.df.500, "rut.summary.500.tableV2.csv", row.names = F)
write.csv(summary.wi.df.500, "winter.forage.summary.table.500V2.csv", row.names = F)
write.csv(summary.fa.df.500, "fawning.summary.table.500V2.csv", row.names = F)
write.csv(summary.su.df.500, "summer.forage.summary.table.500V2.csv", row.names = F)
```
# Correlation plots

```{r}
# Correlation plots
library(corrplot)
library(magick)
#https://cran.r-project.org/web/packages/corrplot/vignettes/corrplot-intro.html
# For more sophisticated plots if you ever need them, convert corrplot object into ggplot for customization.
  # https://dk81.github.io/dkmathstats_site/rvisual-corrplots.html


# Setting up new dfs with only covariates that you want
ru.cor.df <- ru.dat.500 %>%
  select(Deer.det, coyote.day, evi.500.wa, temperate.boreal.grassland, shrub.herb.wetland, woody.ag.tree, herbaceous.agriculture, herbaceous.woody.developed, temperate.boreal.forest, developed.lowmed, developed.high)

wi.cor.df <- wi.dat.500 %>%
  select(Deer.det, coyote.day, evi.500.wa, temperate.boreal.grassland, shrub.herb.wetland, woody.ag.tree, herbaceous.agriculture, herbaceous.woody.developed, temperate.boreal.forest, developed.lowmed, developed.high)

fa.cor.df <- fa.dat.500 %>%
  select(Deer.det, coyote.day, evi.500.wa, temperate.boreal.grassland, shrub.herb.wetland, woody.ag.tree, herbaceous.agriculture, herbaceous.woody.developed, temperate.boreal.forest, developed.lowmed, developed.high)

su.cor.df <- su.dat.500 %>%
  select(Deer.det, coyote.day, evi.500.wa, temperate.boreal.grassland, shrub.herb.wetland, woody.ag.tree, herbaceous.agriculture, herbaceous.woody.developed, temperate.boreal.forest, developed.lowmed, developed.high)

# Rename to make it match in text figures
ru.cor.df <- ru.cor.df %>%
  rename("Coyote" = coyote.day, "EVI" = evi.500.wa, "T.B. grassland" = temperate.boreal.grassland, "H.S. wetland" = shrub.herb.wetland, "Woody ag" = woody.ag.tree, "Herb ag" = herbaceous.agriculture, "H.W. developed" = herbaceous.woody.developed, "T.B. forest" = temperate.boreal.forest, "Developed low-med" = developed.lowmed, "Developed high" = developed.high)

wi.cor.df <- wi.cor.df %>%
  rename("Coyote" = coyote.day, "EVI" = evi.500.wa, "T.B. grassland" = temperate.boreal.grassland, "H.S. wetland" = shrub.herb.wetland, "Woody ag" = woody.ag.tree, "Herb ag" = herbaceous.agriculture, "H.W. developed" = herbaceous.woody.developed, "T.B. forest" = temperate.boreal.forest, "Developed low-med" = developed.lowmed, "Developed high" = developed.high)

fa.cor.df <- fa.cor.df %>%
  rename("Coyote" = coyote.day, "EVI" = evi.500.wa, "T.B. grassland" = temperate.boreal.grassland, "H.S. wetland" = shrub.herb.wetland, "Woody ag" = woody.ag.tree, "Herb ag" = herbaceous.agriculture, "H.W. developed" = herbaceous.woody.developed, "T.B. forest" = temperate.boreal.forest, "Developed low-med" = developed.lowmed, "Developed high" = developed.high)

su.cor.df <- su.cor.df %>%
  rename("Coyote" = coyote.day, "EVI" = evi.500.wa, "T.B. grassland" = temperate.boreal.grassland, "H.S. wetland" = shrub.herb.wetland, "Woody ag" = woody.ag.tree, "Herb ag" = herbaceous.agriculture, "H.W. developed" = herbaceous.woody.developed, "T.B. forest" = temperate.boreal.forest, "Developed low-med" = developed.lowmed, "Developed high" = developed.high)

# Get pearson correlations
ru.cors = cor(ru.cor.df, method = "pearson")
wi.cors = cor(wi.cor.df, method = "pearson")
fa.cors = cor(fa.cor.df, method = "pearson")
su.cors = cor(su.cor.df, method = "pearson")

# Manually saving these files, annoying, but works.
plot.new()
png(filename = "prerut.corplot.png", width = 604, height = 554)
ru.cor.plot <- corrplot(ru.cors, method = 'square', type = 'lower', diag = FALSE, tl.col = "black",  tl.cex = 1.2, cl.cex = 1.2, col = COL2("RdBu"))
mtext("Pre-rut/Rut", at=6, line=.5, cex=2) 
dev.off()

plot.new()
png(filename = "winter.corplot.png", width = 604, height = 554)
wi.cor.plot <- corrplot(wi.cors, method = 'square', type = 'lower', diag = FALSE, tl.col = "black",  tl.cex = 1.2, cl.cex = 1.2, col = COL2("RdBu"))
mtext("Winter forage", at=6, line=.5, cex=2) 
dev.off()

plot.new()
png(filename = "fawning.corplot.png", width = 604, height = 554)
fa.cor.plot <- corrplot(fa.cors, method = 'square', type = 'lower', diag = FALSE, tl.col = "black", tl.cex = 1.2, cl.cex = 1.2, col = COL2("RdBu"))
mtext("Fawning", at=6, line=.5, cex=2) 
dev.off()


plot.new()
png(filename = "summer.corplot.png", width = 604, height = 554)
su.cor.plot <- corrplot(su.cors, method = 'square', type = 'lower', diag = FALSE, tl.col = "black", tl.cex = 1.2, cl.cex = 1.2, col = COL2("RdBu"))
mtext("Summer forage", at=6, line=.5, cex=2) 
dev.off()

# bring PNGs back in
ru.cp <- image_read("prerut.corplot.png")
wi.cp <- image_read("winter.corplot.png")
fa.cp <- image_read("fawning.corplot.png")
su.cp <- image_read("summer.corplot.png")

# Next use image_append in magick, may have some resolution and dpi issues though
x <- image_append(c(su.cp, ru.cp), stack = F)
y <- image_append(c(wi.cp, fa.cp), stack = F)

panel.fig <- image_append(c(x,y), stack = T)

image_write(panel.fig, path = "supplemental.figure1.png", format = "png", density = "500")


```